---
title: "Bootstrap PIM"
author: "Han Bossier"
date: "13-8-2017"
output:
  html_document:
    theme: journal
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	comment = NA,
	cache = TRUE,
	warning = FALSE
)
```

## Short Intro

In this report, we try to perform a simple bootstrap on simulated data and construct percentile based 95% confidence intervals using PIM. We will like to look at the emperical coverage.

## Model

The model is based on a simple linear regression simulation set-up.

#### Data generation

```{r "model-1", echo = FALSE}
u <- 1
alpha <- 5
sigma <- 1
trueBeta <- alpha/(sqrt(2) * sigma)
```

We first generate data under the linear model:

$$
Y_i = \alpha X_i + \varepsilon_i 
$$
with $i = 1,...,n$ and $\varepsilon_i$ are i.i.d. $N({0,\sigma^2)}$ with $\sigma^2 = 1$. We consider a sample size $n = 250.000$. The predictor (*X*) is uniformly spaced between $[0.1,1]$. The value $\alpha$ is set to 5. Using the probit link function, the corresponding PIM can be expressed as:

$$
\Phi^{-1}[P(Y\preceq Y'|X,X')] = \beta(X' - X)
$$
where $\beta = \alpha/\sqrt{2\sigma^2}$. Hence the true value for $\beta$ equals ```r 5/(sqrt(2 * 1))```.



## Simulation

In the following code, we load in libraries, set the seed and fix some parameters.

```{r "settings", cache.rebuild = TRUE}
# Libraries
library(pim)
library(tidyverse)

# Seed
set.seed(12345)

# Sample size
n <- 100

# Model
alpha <- 5
sigma <- 1
trueBeta <- alpha/(sqrt(2) * sigma)

# Number of bootstraps
nBoots <- 999

# Number of simulations
nsim <- 100

# Empty data frame containing all data
ALL_bootData <- c()
```

Now we loop over 100 simulations in which we bootstrap for 999 times (**B = 999**). In each bootstrap, we generate a predictor and data according to the model described above. Then we fit a probabilistic index model and save the estiated $\beta$ parameter. 
<br>
After 999 bootstraps, we take the $0.025^{th}$ and $0.975^{th}$ percentile of these estimated $\beta$'s. These are then the lower and upper 95% CI bounds.
<br>
Finally, we check over all simulations whether the true value for $\beta$ is between the bootstrap CI bounds.

```{r "bootstrap", cache = TRUE}
# For loop over the simulations
for(i in 1:nsim){
  # The dataset
  # Generate predictor
  X <- runif(n = n, min = 0.1, max = u)
  # Generate data
  Y <- alpha*X + rnorm(n = n, mean = 0, sd = sigma)
  # In data frame
  OrigData <- data.frame(Y = Y, X = X)
  # Bootstrap vector (within simulation)
  sim_bootData <- c()
  # For loop over the bootstraps
  for(b in 1:nBoots){
    # Sample from dataset
    SelectData <- sample_n(OrigData, size = n, replace = TRUE)
    
    # Fit PIM
    PIMfit <- pim(formula = Y ~ X, data = SelectData,
                      link = 'probit', model = 'difference')
    # Gather data
    variance <- vcov(PIMfit)[1]
    CIlow <- coef(PIMfit) - (qnorm(0.025, lower.tail = FALSE) * sqrt(variance))
    CIup <- coef(PIMfit) + (qnorm(0.025, lower.tail = FALSE) * sqrt(variance))
    bootData <- data.frame('beta' = coef(PIMfit), 'variance' = variance, 
                           'CIlow' = CIlow, 'CIup' = CIup, 'boot' = b)
    
    # In rows
    sim_bootData <- bind_rows(sim_bootData, bootData) %>% tbl_df()
    
    # Reset bootstrap
    rm(bootData)
  }
  # Summarize over simulations
  simData <- data.frame('AvgBeta' = summarise(sim_bootData, AvgBeta = mean(beta)),
             'CIlow' = quantile(sim_bootData$beta, probs = c(0.025), names = FALSE),
             'CIup' = quantile(sim_bootData$beta, probs = c(0.975), names = FALSE),
             'sim' = i)
  simData <- mutate(simData, ind_cov = ifelse(trueBeta >= CIlow & trueBeta <= CIup, 1 ,0))
  
  ALL_bootData <- bind_rows(ALL_bootData, simData)
  
  # Reset bootstrap vectors
  rm(sim_bootData)
}
```


## Results

First we plot all the CI's with the true value for $\beta$ being the vertical line

```{r "plot", fig.align='center', fig.width=8, cache.rebuild=TRUE}
ALL_bootData %>%
  ggplot(., aes(x = trueBeta)) + geom_vline(xintercept = trueBeta) +
  geom_point(aes(x = AvgBeta, y = sim)) + 
  geom_segment(aes(x = CIlow, xend = CIup, y = sim, yend = sim)) + 
  scale_x_continuous("beta") + scale_y_continuous("simulation") +
  ggtitle("95% CI around bootstrap beta PIM estimate")
```

Then, we calculate the emperical coverage.

```{r "coverage", cache.rebuild = TRUE}
summarise(ALL_bootData, EC = mean(ind_cov, na.rm = TRUE))
```



